---
title: "Continuous Did"
author: "Christine Schulz"
date: "April 19, 2022"
output: 
  pdf_document:
    keep_tex: yes
    
tables: true
graphics: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(tidyverse)
library(fixest)
```

```{r}
crime <- read_dta("~/R/replication_project_pols6200/crime.dta")
county <- read_dta("~/R/replication_project_pols6200/county_dict.dta")

refugees <- read_dta("~/R/replication_project_pols6200/wraps_fips.dta")
demographics <- read_dta("~/R/replication_project_pols6200/demographics.dta")
```

run continous treat on year county fixed effects - w refugee number on crime statistics - naive twfe
- give quantity that may or may not be similar to what they find
- this is what they did in the second part of the paper

Continuous DiD Model
```{r}
### making correct data set for continuous did

refugees1 <- refugees %>% 
  filter(year >= "2010")

crime1 <- crime %>%  
  select(state = "state", fips = "fips", year = "year", property_crime = "property_crime", violent_crime = "violent_crime",
         cleared_property_crime = "cleared_property_crime", cleared_violent_crime = "cleared_violent_crime")

ref_crime <- left_join(refugees1, crime1)

cdid <- left_join(ref_crime, demographics) 

#vars
cdid <- cdid %>% 
  mutate(lproperty_crime = log(property_crime + 1),
         rproperty_crime = (property_crime / pop_total) * 100000,
         lviolent_crime = log(violent_crime + 1),
         rviolent_crime = (violent_crime / pop_total) * 100000,
         lrefugees = log(refugees + 1),
         rrefugees = (refugees / pop_total) * 100,
         s_movers = (pop_moved_in_1_yr_ago / pop_total) * 100000,
         l_movers = log(pop_moved_in_1_yr_ago + 1),
         s_clr_property = cleared_property_crime / property_crime,
         s_clr_violent = cleared_violent_crime / violent_crime,
         log_pop_total = log(pop_total),
         log_pop_density <- log(pop_density))
 
#creating trt based on if year is2017 and 2016 value for median - transformed refugee var
cdid <- cdid %>% 
  group_by(fips) %>% 
  arrange(year) %>% 
  mutate(treatedr = ifelse(year == 2017 & lag(rrefugees) > median(rrefugees), 1, 0)) %>% 
  mutate(treatedr = ifelse(year == 2018 & lag(rrefugees, 2) > median(rrefugees), 1, treatedr))

cdid <- cdid %>% 
  group_by(fips) %>% 
  arrange(year) %>% 
  mutate(treatedl = ifelse(year == 2017 & lag(lrefugees) > median(lrefugees), 1, 0)) %>% 
  mutate(treatedl = ifelse(year == 2018 & lag(lrefugees, 2) > median(lrefugees), 1, treatedl))

```


```{r}
##continous did models - with all years & no dummy interacted for year
  #still need to add county-specific linear time trends allowing
  #for idiosyncratic trends across localities

#regular
cdidr_pcrime <- feols(rproperty_crime ~ treatedr | fips + year, cluster = "state", cdid)
summary(cdidr_pcrime)


cdidr_pcrimec <- feols(rproperty_crime ~ treatedr  + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid)
summary(cdidr_pcrimec)

cdidr_vcrime <- feols(rviolent_crime ~ treatedr | fips 
                      + year, cluster = "state", cdid)
summary(cdidr_vcrime)

cdidr_vcrimec <- feols(rviolent_crime ~ treatedr + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid)
summary(cdidr_vcrimec)

#log
cdidl_pcrime <- feols(lproperty_crime ~ treatedl | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_pcrime)

cdidl_pcrimec <- feols(lproperty_crime ~ treatedl + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad 
                       + s_hs_dropout | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_pcrimec)

cdidl_vcrime <- feols(lviolent_crime ~ treatedl | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_vcrime)

cdidl_vcrimec <- feols(lviolent_crime ~ treatedl + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_vcrimec)
```
coeficient plot
```{r}
#plot summs
library(jtools)
library(ggstance)
plot_summs(cdidr_pcrime, cdidr_vcrime, cdidl_vcrime, cdidl_pcrime, 
           coefs = c("Refugee Arrivals" = "treatedr", 
                     "Log Refugee Arrivals" = "treatedl"),
           model.names = c("Property Crime", "Violent Crime", 
                           "Log Property Crime", "Log Violent Crime"))
```

```{r}

plot_summs(cdidr_pcrimec, cdidr_vcrimec, cdidl_vcrimec, cdidl_pcrimec, 
           coefs = c("Refugee Arrivals" = "treatedr", 
                     "Log Refugee Arrivals" = "treatedl",
                     "Population Total" = "pop_total",
                 "Share White Pop." = "s_white", "Share Black Pop." = "s_black",
                 "Share Hispanic Pop." = "s_hisp", "Unemployment Rate" = "s_unempl",
                 "Males Aged 15-34" = "s_male_age_15_34", 
                 "Highschool Graduate" = "s_hs_grad",
                 "Highschool Dropout" = "s_hs_dropout", 
                 "Out of Labor Force" = "s_not_in_lf"),
           model.names = c("Property Crime", "Violent Crime", 
                           "Log Property Crime", "Log Violent Crime"))


```



event study plot main results
```{r}

# Use i() in feols to include time dummies,
# specifying that we want to drop t = 5 as the reference

#create fake treatment vars - this one works i think
cdid <- cdid %>% 
  mutate(fakeTreat = ifelse(treatedr %in% "0", 1, 1 ))

m <- feols(rproperty_crime ~ i(year, fakeTreat, ref = 2016) | state, data = cdid)
coefplot(m, pt.join = TRUE, ref.line = TRUE)

m1 <- feols(rviolent_crime ~ i(year, fakeTreat, ref = 2016) | state, data = cdid)
coefplot(m1, pt.join = TRUE, ref.line = TRUE)

m2 <- feols(lproperty_crime ~ i(year, fakeTreat, ref = 2016) | state, data = cdid)
coefplot(m2, pt.join = TRUE, ref.line = TRUE)

m3 <- feols(lviolent_crime ~ i(year, fakeTreat, ref = 2016) | state, data = cdid)
coefplot(m3, pt.join = TRUE, ref.line = TRUE)

```

```{r, results='asis'}
setFixest_dict(c(rproperty_crime = "Property Crime", 
                 lproperty_crime = "Log Property Crime",
                 treatedr = "Refugee Arrivals",
                 treatedl = "Log Refugee Arrivals",
                 fips = "County",
                 fyear = "Year",
                 lviolent_crime = "Log Violent Crime",
                 rviolent_crime = "Violent Crime",
                 pop_total = "Population Total",
                 s_white = "Share White Pop.", s_black = "Share Black Pop.",
                 s_hisp = "Share Hispanic Pop.", 
                 s_unempl = "Unemployment Rate",
                 s_male_age_15_34 = "Males Aged 15-34", 
                 s_hs_grad = "Highschool Graduate",
                 s_hs_dropout = "Highschool Dropout", 
                 s_not_in_lf = "Out of Labor Force",
                 s_police_male = "Male Police",
                 s_clr_property = "Cleared Property Crime",
                 s_clr_violent = "Cleared Violent Crime",
                 l_movers = "Log In-Movers",
                 s_movers = "In-Movers"))

my_style <- style.df(depvar.title = "", fixef.title = "",
                     fixef.suffix = " Fixed Effects", yesNo = "yes")
setFixest_etable(style.df = my_style)

styling = function(x, font){
  tex2add = ""
  if(!missing(font)){
    tex2add = paste0("\\footnotesize")
    }
  if(nchar(tex2add) > 0){
    x[x == "%start:tab\n"] = tex2add
    }
  x
}

```
# estimates without controls
```{r, results='asis'}

etable(cdidr_pcrime, cdidr_vcrime, cdidl_vcrime, cdidl_pcrime, 
       fitstat = ~n,
       postprocess.tex = styling,
       font = "footnotesize",
       tex = TRUE,
       style.tex = style.tex("aer"),
       title = "The Executive Order on Local Crime Rates: 
       Differences-in-Differences, 2015-2018")

```
estimates with controls
```{r, results='asis'}
etable(cdidr_pcrimec, cdidr_vcrimec, cdidl_vcrimec, cdidl_pcrimec, 
       fitstat = ~n,
       postprocess.tex = styling,
       font = "footnotesize",
       tex = TRUE,
       style.tex = style.tex("aer"),
       title = "The Executive Order on Local Crime Rates: 
       Differences-in-Differences, 2015-2018")
```
Regular estimates and regular estimates with controls
```{r, results='asis'}

etable(cdidr_pcrime, cdidr_pcrimec, cdidr_vcrime, cdidr_vcrimec, 
       fitstat = ~n,
       postprocess.tex = styling,
       font = "footnotesize",
       tex = TRUE,
       style.tex = style.tex("aer"),
       title = "The Executive Order on Local Crime Rates: 
       Differences-in-Differences, 2015-2018")

```
Log estimates and log estimates with controls
```{r, results = 'asis'}

etable(cdidl_pcrime, cdidl_pcrimec, cdidl_vcrime, cdidl_vcrimec, 
       fitstat = ~n,
       postprocess.tex = styling,
       font = "footnotesize",
       tex = TRUE,
       style.tex = style.tex("aer"),
       title = "The Executive Order on Local Crime Rates: 
       Differences-in-Differences, 2015-2018")
```

Additional specifications done by the author

```{r}
#subset to urban counties

cdid <- cdid %>%  
  mutate(ntile = ntile(pop_density, 2),
         urban = ifelse(ntile >= "2", 1, 0))

cdid2 <- cdid %>% 
  filter(urban %in% "1")

#regular
cdidr_pcrime1 <- feols(rproperty_crime ~ treatedr | fips 
                      + year, cluster = "state", cdid2)
summary(cdidr_pcrime1)

cdidr_pcrime1c <- feols(rproperty_crime ~ treatedr + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad 
                       + s_hs_dropout | year + fips, cluster = "state", cdid2)
summary(cdidr_pcrime1c)

cdidr_vcrime1 <- feols(rviolent_crime ~ treatedr | fips 
                      + year, cluster = "state", cdid2)
summary(cdidr_vcrime1)

cdidr_vcrime1c <- feols(rviolent_crime ~ treatedr + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid2)
summary(cdidr_vcrime1c)

#log
cdidl_pcrime1 <- feols(lproperty_crime ~ treatedl | fips 
                      + year, cluster = "state", cdid2)
summary(cdidl_pcrime1)

cdidl_pcrime1c <- feols(lproperty_crime ~ treatedl + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad 
                       + s_hs_dropout | fips 
                      + year, cluster = "state", cdid2)
summary(cdidl_pcrime1c)

cdidl_vcrime1 <- feols(lviolent_crime ~ treatedl | fips 
                      + year, cluster = "state", cdid2)
summary(cdidl_vcrime1)

cdidl_vcrime1c <- feols(lviolent_crime ~ treatedl + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid2)
summary(cdidl_vcrime1c)

```

```{r, results = 'asis'}

etable(cdidr_pcrime1, cdidr_vcrime1, cdidl_pcrime1, cdidl_vcrime1,
       fitstat = ~n,
       postprocess.tex = styling,
       font = "footnotesize",
       tex = TRUE,
       style.tex = style.tex("aer"),
       title = "Differences-in-Differences Estimates Subsetted to 
       Urban Counties, 2015-2018")
```

```{r, results = 'asis'}

etable(cdidr_pcrime1c, cdidr_vcrime1c, cdidl_pcrime1c, cdidl_vcrime1c, 
       fitstat = ~n,
       postprocess.tex = styling,
       font = "footnotesize",
       tex = TRUE,
       style.tex = style.tex("aer"),
       title = "Differences-in-Differences Log Estimates Subsetted to 
       Urban Counties, 2015-2018")
```
Coefficient plot - subset to urban counties
```{r}
#models w controls
plot_summs(cdidr_pcrime1, cdidr_vcrime1, cdidl_vcrime1, cdidl_pcrime1, 
           coefs = c("Refugee Arrivals" = "treatedr", 
                     "Log Refugee Arrivals" = "treatedl"),
           model.names = c("Property Crime", "Violent Crime", 
                           "Log Property Crime", "Log Violent Crime"))


#models w controls
plot_summs(cdidr_pcrime1c, cdidr_vcrime1c, cdidl_vcrime1c, cdidl_pcrime1c, 
           coefs = c("Refugee Arrivals" = "treatedr", 
                     "Log Refugee Arrivals" = "treatedl",
                     "Population Total" = "pop_total",
                 "Share White Pop." = "s_white", "Share Black Pop." = "s_black",
                 "Share Hispanic Pop." = "s_hisp", "Unemployment Rate" = "s_unempl",
                 "Males Aged 15-34" = "s_male_age_15_34", 
                 "Highschool Graduate" = "s_hs_grad",
                 "Highschool Dropout" = "s_hs_dropout", 
                 "Out of Labor Force" = "s_not_in_lf"),
           model.names = c("Property Crime", "Violent Crime", 
                           "Log Property Crime", "Log Violent Crime"))

```

Share male police as outcome
```{r}
##models with dummy for year interacted with dummy var for refugees
#regular
cdidr_police <- feols(s_police_male ~ treatedr | fips 
                      + year, cluster = "state", cdid)
summary(cdidr_police)

cdidr_policec <- feols(s_police_male ~ treatedr + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | year + fips, cluster = "state", cdid)
summary(cdidr_policec)


#log
cdidl_police <- feols(s_police_male ~ treatedl | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_police)

cdidl_policec <- feols(s_police_male ~ treatedl + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_policec)

```

```{r, results = 'asis'}

etable(cdidr_police, cdidr_policec, cdidl_police, cdidl_policec,
       fitstat = ~n,
       postprocess.tex = styling,
       font = "footnotesize",
       tex = TRUE,
       style.tex = style.tex("aer"),
       title = "The Executive Order on Male Police: 
       Differences-in-Differences, 2015-2018")
```
Coefficient plot - share male police
```{r}
#models w controls
plot_summs(cdidr_police, cdidl_police, 
           coefs = c("Refugee Arrivals" = "treatedr", 
                     "Log Refugee Arrivals" = "treatedl"),
           model.names = c("Male Police", "Log Male Police"))

#models w controls
plot_summs(cdidr_policec, cdidl_policec, 
           coefs = c("Refugee Arrivals" = "treatedr", 
                     "Log Refugee Arrivals" = "treatedl",
                     "Population Total" = "pop_total",
                 "Share White Pop." = "s_white", "Share Black Pop." = "s_black",
                 "Share Hispanic Pop." = "s_hisp", "Unemployment Rate" = "s_unempl",
                 "Males Aged 15-34" = "s_male_age_15_34", 
                 "Highschool Graduate" = "s_hs_grad",
                 "Highschool Dropout" = "s_hs_dropout", 
                 "Out of Labor Force" = "s_not_in_lf",
                 "Male Police" = "s_police_male"),
           model.names = c("Male Police", "Log Male Police"))

```

share in movers as outcome
```{r}
##models with dummy for year interacted with dummy var for refugees
#regular
cdidr_movers <- feols(s_movers ~ treatedr | fips 
                      + year, cluster = "state", cdid)
summary(cdidr_movers)

cdidr_moversc <- feols(s_movers ~ treatedr + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | year + fips, cluster = "state", cdid)
summary(cdidr_moversc)


#log
cdidl_movers <- feols(l_movers ~ treatedl | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_movers)

cdidl_moversc <- feols(l_movers ~ treatedl + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_moversc)

```

```{r, results = 'asis'}

etable(cdidr_movers, cdidr_moversc, cdidl_movers, cdidl_moversc,
       fitstat = ~n,
       postprocess.tex = styling,
       font = "footnotesize",
       tex = TRUE,
       style.tex = style.tex("aer"),
       title = "The Executive Order on Share of In-Movers: 
       Differences-in-Differences, 2015-2018")
```

Coefficient plot - movers
```{r}
#models w controls
plot_summs(cdidr_movers, cdidl_movers, 
           coefs = c("Refugee Arrivals" = "treatedr", 
                     "Log Refugee Arrivals" = "treatedl"),
           model.names = c("In-Movers", "Log In-Movers"))

#models w controls
plot_summs(cdidr_moversc, cdidl_moversc, 
           coefs = c("Refugee Arrivals" = "treatedr", 
                     "Log Refugee Arrivals" = "treatedl",
                     "Population Total" = "pop_total",
                 "Share White Pop." = "s_white", "Share Black Pop." = "s_black",
                 "Share Hispanic Pop." = "s_hisp", "Unemployment Rate" = "s_unempl",
                 "Males Aged 15-34" = "s_male_age_15_34", 
                 "Highschool Graduate" = "s_hs_grad",
                 "Highschool Dropout" = "s_hs_dropout", 
                 "Out of Labor Force" = "s_not_in_lf",
                 "Male Police" = "s_police_male"),
           model.names = c("In-Movers", "Log In-Movers"))

```

Share cleared crimes as outcome

```{r}
##models with dummy for year interacted with dummy var for refugees
#regular
cdidr_clr_pcrime <- feols(s_clr_property ~ treatedr | fips 
                      + year, cluster = "state", cdid)
summary(cdidr_clr_pcrime)

cdidr_clr_pcrimec <- feols(s_clr_property ~ treatedr + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad 
                       + s_hs_dropout | year + fips, cluster = "state", cdid)
summary(cdidr_clr_pcrimec)

cdidr_clr_vcrime <- feols(s_clr_violent ~ treatedr | fips 
                      + year, cluster = "state", cdid)
summary(cdidr_clr_vcrime)

cdidr_clr_vcrimec <- feols(s_clr_violent ~ treatedr + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad
                       + s_hs_dropout | fips 
                      + year, cluster = "state", cdid)
summary(cdidr_clr_vcrimec)

#log
cdidl_clr_pcrime <- feols(s_clr_property ~ treatedl | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_clr_pcrime)

cdidl_clr_pcrimec <- feols(s_clr_property ~ treatedl + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad
                       + s_hs_dropout | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_clr_pcrimec)

cdidl_clr_vcrime <- feols(s_clr_violent ~ treatedl | fips 
                      + year, cluster = "state", cdid)
summary(cdidl_clr_vcrime)

cdidl_clr_vcrimec <- feols(s_clr_violent ~ treatedl + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad
                       + s_hs_dropout | fips 
                      + year, cluster = "state", cdid)



```

```{r, results = 'asis'}

etable(cdidr_clr_pcrime, cdidl_clr_pcrime, cdidr_clr_vcrime, cdidl_clr_vcrime, 
       fitstat = ~n,
       postprocess.tex = styling,
       font = "footnotesize",
       tex = TRUE,
       style.tex = style.tex("aer"),
       title = "The Executive Order on Cleared Crime: 
       Differences-in-Differences, 2015-2018")
```

Cleared crime with controls 
```{r, results = 'asis'}

etable(cdidr_clr_pcrimec, cdidl_clr_pcrimec, cdidr_clr_vcrimec, cdidl_clr_vcrimec,
       fitstat = ~n,
       postprocess.tex = styling,
       font = "footnotesize",
       tex = TRUE,
       style.tex = style.tex("aer"),
       title = "The Executive Order on Cleared Crime with Controls: 
       Differences-in-Differences, 2015-2018")
```

Coefficient plot - cleared crime
```{r}
#models w controls
plot_summs(cdidr_clr_pcrime, cdidr_clr_vcrime, cdidl_clr_vcrime, cdidl_clr_pcrime, 
           coefs = c("Refugee Arrivals" = "treatedr", 
                     "Log Refugee Arrivals" = "treatedl"),
           model.names = c("Cleared Property Crime", "Cleared Violent Crime", 
                           "Log Cleared Property Crime", "Log Cleared Violent Crime"))

#models w controls
plot_summs(cdidr_clr_pcrimec, cdidr_clr_vcrimec, cdidl_clr_vcrimec, cdidl_clr_pcrimec, 
           coefs = c("Refugee Arrivals" = "treatedr", 
                     "Log Refugee Arrivals" = "treatedl",
                     "Population Total" = "pop_total",
                 "Share White Pop." = "s_white", "Share Black Pop." = "s_black",
                 "Share Hispanic Pop." = "s_hisp", "Unemployment Rate" = "s_unempl",
                 "Males Aged 15-34" = "s_male_age_15_34", 
                 "Highschool Graduate" = "s_hs_grad",
                 "Highschool Dropout" = "s_hs_dropout", 
                 "Out of Labor Force" = "s_not_in_lf",
                 "Male Police" = "s_police_male"),
           model.names = c("Cleared Property Crime", "Cleared Violent Crime", 
                           "Log Cleared Property Crime", "Log Cleared Violent Crime"))

```