---
title: "repication project extra code"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

```{r}
crime <- read_dta("~/R/replication_project_pols6200/crime.dta")
county <- read_dta("~/R/replication_project_pols6200/county_dict.dta")

refugees <- read_dta("~/R/replication_project_pols6200/wraps_fips.dta")
demographics <- read_dta("~/R/replication_project_pols6200/demographics.dta")
```

creating variables the long way for the replication project

```{r}
#creating dataset with all necessary vars that I can use for other analyses instead
  #of creating new vars each time

crime1 <- crime %>%  
  select(state = "state", fips = "fips", year = "year", property_crime = "property_crime", violent_crime = "violent_crime",
         cleared_property_crime = "cleared_property_crime", cleared_violent_crime = "cleared_violent_crime")

ref_crime1 <- left_join(refugees, crime1)

ref_crime <- left_join(ref_crime1, demographics) 

#vars

ref_crime$lproperty_crime <- log(ref_crime$property_crime + 1)

ref_crime$rproperty_crime <- (ref_crime$property_crime / ref_crime$pop_total) * 100000

ref_crime$lviolent_crime <- log(ref_crime$violent_crime + 1)

ref_crime$rviolent_crime <- (ref_crime$violent_crime / ref_crime$pop_total) * 100000

ref_crime$lrefugees <- log(ref_crime$refugees + 1)

ref_crime$rrefugees <- (ref_crime$refugees / ref_crime$pop_total) * 100

#other vars that i dont know where they go/what they do

ref_crime$s_movers <- (ref_crime$pop_moved_in_1_yr_ago / ref_crime$pop_total) * 100000

ref_crime$l_movers <- log(ref_crime$pop_moved_in_1_yr_ago + 1)

ref_crime$s_clr_property <- ref_crime$cleared_property_crime / ref_crime$property_crime

ref_crime$s_clr_violent <- ref_crime$cleared_violent_crime / ref_crime$violent_crime

#might need to change this to just log in 2016
ref_crime$log_pop_total <- log(ref_crime$pop_total)

ref_crime$log_pop_density <- log(ref_crime$pop_density)



```

First differences bullshit
```{r}
#andrew heiss and class manual DiD 

fdiff2 <- fdiff %>% 
  group_by(fyear, fips) %>% 
  summarize(lproperty_crime = sum(lproperty_crime),
            rproperty_crime = sum(rproperty_crime),
            rviolent_crime = sum(rviolent_crime),
            lviolent_crime = sum(lviolent_crime),
            rrefugees = sum(rrefugees),
            lrefugees = sum(lrefugees),
            pop_total = sum(pop_total),
            pop_density = sum(pop_density),
            s_black = sum(s_black),
            s_hisp = sum(s_hisp), 
            s_hs_dropout = sum(s_hs_dropout),
            s_unempl = sum(s_unempl),
            s_not_in_lf = sum(s_not_in_lf),
            s_white = sum(s_white),
            s_police_male = sum(s_police_male),
            s_movers = sum(s_movers),
            s_hs_grad = sum(s_hs_grad),
            s_male_age_15_34 = sum(s_male_age_15_34),
            l_movers = sum(l_movers),
            s_clr_property = sum(s_clr_property),
            s_clr_violent = sum(s_clr_violent))


#creating trt based on if year is2017 and 2016 value for median - transformed refugee var
fdiff2 <- fdiff2 %>% 
  group_by(fips) %>% 
  arrange(fyear) %>% 
  mutate(treatedr = ifelse(fyear == 2017 & lag(rrefugees) > median(rrefugees), 1, 0)) 

fdiff2 <- fdiff2 %>% 
  group_by(fips) %>% 
  arrange(fyear) %>% 
  mutate(treatedl = ifelse(fyear == 2017 & lag(lrefugees) > median(lrefugees), 1, 0)) 

fdiff2$after_2017 <- ifelse(fdiff2$fyear == "2017", 1, 0)

diffs <- fdiff2 %>% 
  group_by(after_2017, treatedr) %>% 
  summarize(mean_rproperty_crime = mean(rproperty_crime, na.rm=T))

before_treatment <- diffs %>% 
  filter(after_2017 == 0, treatedr == 1) %>% 
  pull(mean_rproperty_crime)

before_control <- diffs %>% 
  filter(after_2017 == 0, treatedr == 0) %>% 
  pull(mean_rproperty_crime)

after_treatment <- diffs %>% 
  filter(after_2017 == 1, treatedr == 1) %>% 
  pull(mean_rproperty_crime)

after_control <- diffs %>% 
  filter(after_2017 == 1, treatedr == 0) %>% 
  pull(mean_rproperty_crime)

diff_treatment_before_after <- after_treatment - before_treatment
diff_treatment_before_after


#calculating the first difference then running a basic regression like the internet showed me

fdiff3 <- fdiff1 %>% 
  group_by(fips) %>% 
  mutate(d_rpcrime = diff(rproperty_crime), lag=1,
         d_rvcrime = diff(rviolent_crime), lag =1,
         d_rrefugees = diff(rrefugees), lag =1,
         d_lpcrime = diff(lproperty_crime), lag=1,
         d_lvcrime = diff(lviolent_crime), lag=1,
         d_lrefugees = diff(lrefugees), lag=1,
         d_s_movers = diff(s_movers), lag=1,
         d_l_movers = diff(l_movers), lag =1,
         d_s_clr_property = diff(s_clr_property), lag=1,
         d_s_clr_violent = diff(s_clr_violent), lag=1,
         d_trt_r = diff(trt_r), lag=1,
         d_trt_l = diff(trt_l), lag=1) 


m2 <- feols(d_rpcrime ~ d_trt_r, fdiff3)
summary(m2)

##first difference pool data in 2016 and 2017 by mean of obs

fdiff4 <- fdiff_dta %>% 
  group_by(fyear, fips) %>% 
  summarize(lproperty_crime = mean(lproperty_crime),
            rproperty_crime = mean(rproperty_crime),
            rviolent_crime = mean(rviolent_crime),
            lviolent_crime = mean(lviolent_crime),
            rrefugees = mean(rrefugees),
            lrefugees = mean(lrefugees),
            pop_total = mean(pop_total),
            pop_density = mean(pop_density),
            s_black = mean(s_black),
            s_hisp = mean(s_hisp), 
            s_hs_dropout = mean(s_hs_dropout),
            s_unempl = mean(s_unempl),
            s_not_in_lf = mean(s_not_in_lf),
            s_white = mean(s_white),
            s_police_male = mean(s_police_male),
            s_movers = mean(s_movers),
            s_hs_grad = mean(s_hs_grad),
            s_male_age_15_34 = mean(s_male_age_15_34),
            l_movers = mean(l_movers),
            s_clr_property = mean(s_clr_property),
            s_clr_violent = mean(s_clr_violent))

trt_dta <- fdiff4 %>% 
  filter(fyear %in% "2016") %>% 
  summarize(medianr = median(rrefugees),
            medianl =  median(lrefugees)) %>% 
  View()


fdiff4$trt_r <- ifelse(fdiff4$rrefugees >= "0.001281953" & fdiff4$fyear == "2017", 1, 0 )

fdiff4$trt_l  <- ifelse(fdiff4$lrefugees >= "0.804719" & fdiff4$fyear == "2017", 1, 0)



rpcrime <- feols(rproperty_crime ~ trt_r | fips + fyear, cluster = "fips", fdiff4) 
summary(m3)


#first difference pool data in 2016 and 2017 by summing obs

fdiff1 <- fdiff %>% 
  group_by(fyear, fips) %>% 
  summarize(lproperty_crime = sum(lproperty_crime),
            rproperty_crime = sum(rproperty_crime),
            rviolent_crime = sum(rviolent_crime),
            lviolent_crime = sum(lviolent_crime),
            rrefugees = sum(rrefugees),
            lrefugees = sum(lrefugees),
            pop_total = sum(pop_total),
            pop_density = sum(pop_density),
            s_black = sum(s_black),
            s_hisp = sum(s_hisp), 
            s_hs_dropout = sum(s_hs_dropout),
            s_unempl = sum(s_unempl),
            s_not_in_lf = sum(s_not_in_lf),
            s_white = sum(s_white),
            s_police_male = sum(s_police_male),
            s_movers = sum(s_movers),
            s_hs_grad = sum(s_hs_grad),
            s_male_age_15_34 = sum(s_male_age_15_34),
            l_movers = sum(l_movers),
            s_clr_property = sum(s_clr_property),
            s_clr_violent = sum(s_clr_violent))

trt_dta <- fdiff1 %>% 
  filter(fyear %in% "2016") %>% 
  summarize(medianr = median(rrefugees),
            medianl =  median(lrefugees)) %>% 
  View()

fdiff1$trt_r <- ifelse(fdiff1$rrefugees >= "0.002563905" & fdiff1$fyear == "2017", 1, 0 )

fdiff1$trt_l  <- ifelse(fdiff1$lrefugees >= "1.609438" & fdiff1$fyear == "2017", 1, 0)

m1 <- feols(rproperty_crime ~ trt_r | fips + fyear, cluster = "fips", fdiff1) 
summary(m1)


#not sure how this works tho

df1 <- fdiff %>% 
  select(c(year, fyear, fips, rproperty_crime, rproperty_crime)) %>% 
  group_by(fyear) %>% 
  mutate(diff = diff(rproperty_crime), lag=2) %>% 
  View()
```

Trying synthetic controls

```{r}
library(tidysynth)

crime <- crime %>%  
  select(state = "state", fips = "fips", year = "year", property_crime = "property_crime", violent_crime = "violent_crime",
         cleared_property_crime = "cleared_property_crime", cleared_violent_crime = "cleared_violent_crime")

ref_crime <- left_join(refugees, crime)

dta <- left_join(ref_crime, demographics) 

#transformation outcome var for analysis - log and per capita

dta$lproperty_crime <- log(dta$property_crime + 1)

dta$rproperty_crime <- (dta$property_crime / dta$pop_total) * 100000

dta$lviolent_crime <- log(dta$violent_crime + 1)

dta$rviolent_crime <- (dta$violent_crime / dta$pop_total) * 100000

# treatment variables for the year 2016
  #getting the per capita and log values for refugees
dta$rrefugees <- (dta$refugees / dta$pop_total) * 100
dta$lrefugees <- log(dta$refugees + 1)

#other vars that i dont know where they go/what they do

dta$s_movers <- (dta$pop_moved_in_1_yr_ago / dta$pop_total) * 100000

dta$l_movers <- log(dta$pop_moved_in_1_yr_ago + 1)

dta$s_clr_property <- dta$cleared_property_crime / dta$property_crime

dta$s_clr_violent <- dta$cleared_violent_crime / dta$violent_crime

#might need to change this to just log in 2016
dta$log_pop_total <- log(dta$pop_total)

dta$log_pop_density <- log(dta$pop_density)

refugees_out <-
  fdiff_dta %>%
  synthetic_control(outcome = rproperty_crime, 
                    unit = county, 
                    time = year, 
                    i_unit = county, 
                    i_time = 2017, 
                    generate_placebos=T 
  ) %>%

  generate_predictor(time_window = 2010:2017,
                     povrate_1 = mean(povrate, na.rm=T),
                     unemployment_1 = mean(unemployment, na.rm = T),
                     healthspendpc_1 = mean(healthspendpc, na.rm = T)) %>%

  generate_predictor(time_window = 2000,
                     no_health_ins_capita_2000 = no_health_ins_capita) %>%
  generate_predictor(time_window = 2002,
                     no_health_ins_capita_2002 = no_health_ins_capita) %>%
  generate_predictor(time_window = 2005,
                     no_health_ins_capita_2005 = no_health_ins_capita) %>%

  generate_weights(optimization_window = 2000:2011, 
                   margin_ipop = .02,sigf_ipop = 7,bound_ipop = 6 
  ) %>%
  
  generate_control()

health_out %>% plot_trends()
health_out %>% plot_differences()
health_out %>% plot_weights()
health_out %>% plot_placebos()

```

Continuous DiD
```{r}
##continuous did - just years 2016 to 2017 in the model

cdid1 <- cdid %>% 
  filter(year %in% c("2016", "2017"))

#regular
cdidr_pcrime3 <- feols(rproperty_crime ~ treatedr | fips 
                      + year, cluster = "state", cdid1)
summary(cdidr_pcrime3)

cdidr_pcrime3c <- feols(rproperty_crime ~ treatedr  + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid1)
summary(cdidr_pcrime3c)


cdidr_vcrime3 <- feols(rviolent_crime ~ treatedr | fips 
                      + year, cluster = "state", cdid1)
summary(cdidr_vcrime3)

cdidr_vcrime3c <- feols(rviolent_crime ~ treatedr + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid1)
summary(cdidr_vcrime3c)

#log
cdidl_pcrime3 <- feols(lproperty_crime ~ treatedl | fips 
                      + year, cluster = "state", cdid1)
summary(cdidl_pcrime3)

cdidl_pcrime3c <- feols(lproperty_crime ~ treatedl + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid1)
summary(cdidl_pcrime3c)

cdidl_vcrime3 <- feols(lviolent_crime ~ treatedl | fips 
                      + year, cluster = "state", cdid1)
summary(cdidl_vcrime3)

cdidl_vcrime3c <- feols(lviolent_crime ~ treatedl + pop_total 
                       + s_white + s_black + s_hisp + s_unempl
                       + s_not_in_lf + s_male_age_15_34 + s_hs_grad + s_hs_dropout | fips 
                      + year, cluster = "state", cdid1)
summary(cdidl_vcrime3c)

```

event study plot
```{r}
cdid <- cdid %>% 
  mutate(t = case_when(
    year == "2010" ~ 1,
    year == "2011" ~ 2,
    year == "2012" ~ 3,
    year == "2013" ~ 4,
    year == "2014" ~ 5, 
    year == "2015" ~ 6,
    year == "2016" ~ 7,
    year == "2017" ~ 8,
    year == "2018" ~ 9
  ))

coefplot(m, drop = '(Intercept)',
         pt.join = TRUE, ref = c('t:7' = 8), ref.line = TRUE)

m <- feols(rproperty_crime ~ i(year, ref = 2016), data = cdid,
           cluster = 'fips')

#create fake treatment vars - this one works i think
cdid <- cdid %>% 
  mutate(fakeTreat = ifelse(treatedr %in% "0", 1, 1 ))

m <- feols(rproperty_crime ~ i(year, fakeTreat, ref = 2016) | state, data = cdid)

coefplot(m)


```

Another way to do the coefficient plot
```{r}
library(dotwhisker)
dwplot(list(cdidr_pcrime, cdidr_vcrime, cdidl_pcrime, cdidl_vcrime),
       vline = geom_vline(
           xintercept = 0,
           colour = "grey60",
           linetype = 2
       ),
       vars_order = c("treatedr", "treatedl"),
       model_order = c("Model 1", "Model 2", 
                       "Model 3", "Model 4")
       ) %>% # plot line at zero _behind_coefs
    relabel_predictors(
        c(  treatedr = "Refugee Arrivals",
            treatedl = "Log Refugee Arrivals"
        )
    ) +
    theme_bw(base_size = 4) + 
    # Setting `base_size` for fit the theme
    # No need to set `base_size` in most usage
    xlab("Coefficient Estimate") + ylab("") +
    geom_vline(xintercept = 0,
               colour = "grey60",
               linetype = 2) +
    ggtitle("Continuous Differences Estimates") +
    theme(
        plot.title = element_text(face = "bold"),
        legend.position = c(0.007, 0.01),
        legend.justification = c(0, 0),
        legend.background = element_rect(colour = "grey80"),
        legend.title = element_blank()
    )

```

coeff plots - dont work
```{r}
library(dotwhisker)
library(broom)

fd_rpcrime <- fd_rpcrime %>% broom::tidy() %>% mutate(model = "First Differences")

map2_df(list(fd_rpcrime, fd_rvcrime, fd_lpcrime, fd_lvcrime), 
        c("Property Crime", "Violent Crime", "Log Property Crime",
          "Log Violent Crime"), 
        function(x, y) broom::tidy(x) %>% mutate(model = y)) %>% 
  filter(term %in% c("treatedr", "treatedl", "rproperty_crime",
                     "rviolent_crime", "lproperty_crime", "lviolent_crime")) %>% 
  dwplot() +
  theme_minimal()

```

Descriptive statistics
the map
```{r}
library(sf)
library(rgdal)
library(maps)
library(purrr)

city_mapping <- read_dta("~/R/replication_project_pols6200/citymapping.dta")

fips1 <- county.fips
fips <- map_data("county")
crime <- read_dta("~/R/replication_project_pols6200/crime.dta")

fips1 <- fips1 %>% 
  separate(polyname, into = c("region", "county"), sep = ",") 

fips2 <- left_join(fips, fips1)

#change names after
#dta2 <- left_join(replication, caughey_warshaw, by = c("year", "st.abb" = "stpo"))


ggplot(dma.df, aes(x=long, y=lat, group=group, fill=sinclair_total)) + 
  geom_polygon(color="#666666", size=.5) +
  scale_fill_gradient(low = "white", high="red")+
  geom_polygon(data = states_map, aes(x = long, y = lat, group = group), fill=NA, color="black") + # states' borders
  geom_polygon(data = new.sinclair, 
               aes(x=long, y=lat, group=group), 
               fill = "dodgerblue", color="#666666", size=.5) + # newly acquired stations
  coord_map() +
  theme_void() +
  theme(legend.position="none") 

```

# Table A2: Pre-existing Crime Trends and Dropin Refugee Arrivals: Regression Results
```{r}
pretrends1 <- pretrends %>% 
  filter(year %in% c("2010":"2016"))

#creating trt based on if year is 2017 and 2016 value for median - transformed refugee var
pretrends1 <- pretrends1 %>% 
  group_by(fips) %>% 
  arrange(year) %>% 
  mutate(treatedr = ifelse(year == 2017 & lag(rrefugees) > median(rrefugees), 1, 0)) %>% 
  mutate(treatedr = ifelse(year == 2018 & lag(rrefugees, 2) > median(rrefugees), 1, treatedr))

pretrends1 <- pretrends1 %>% 
  group_by(fips) %>% 
  arrange(year) %>% 
  mutate(treatedl = ifelse(year == 2017 & lag(lrefugees) > median(lrefugees), 1, 0)) %>% 
  mutate(treatedl = ifelse(year == 2018 & lag(lrefugees, 2) > median(lrefugees), 1, treatedl))

```

Figure A5 Coefficient plot
```{r}


  #binning refugees into trt and control groups
trt_dta <- ref_crime %>% 
  filter(year %in% "2016") %>% 
  summarize(medianr = median(rrefugees),
            medianl =  median(lrefugees)) 

ref_crime$trt_r <- ifelse(ref_crime$rrefugees >= "0.001011693" & ref_crime$year == "2016", 1, 0 )

ref_crime$trt_l  <- ifelse(ref_crime$lrefugees >= "1.098612" & ref_crime$year == "2016", 1, 0)

  #creating a year dummy because that's what they did
ref_crime$year_dummy <- ifelse(ref_crime$year <= "2017", 0, 1)


##models with dummy for year interacted with dummy var for refugees
#regular
dta <- ref_crime %>% 
  filter(year >= "2010")

dta %>% 
  mutate(time_to_trt = case_when(
    year >= "2017" & trt_r == "1" ~ "1",
    year >= "2017" & trt_r == "0" ~ "0",
    year <= "2015" & trt_r == "0" & trt_r == 1 ~ "0",
    year == "2016" & trt_r == "0" & trt_r == 1 ~ "-1"
  ))

ref_crime$time_to_trt <- ifelse(ref_crime$year >= "2016" & ref_crime$trt_r == "1", 1, 0)


rpcrime1 <- feols(rproperty_crime ~ trt_r + year_dummy + trt_r:year_dummy | fips 
                      + year, cluster = "state", ref_crime)

library(eventstudies)

ES_plot_ATTs <- (rpcrime1) 

rvcrime1 <- feols(rviolent_crime ~ trt_r + year_dummy + trt_r:year_dummy | fips 
                      + year, cluster = "state", ref_crime)

#log
lpcrime1 <- feols(lproperty_crime ~ trt_l + year_dummy + trt_l:year_dummy | fips 
                      + year, cluster = "state", ref_crime)

lvcrime1 <- feols(lviolent_crime ~ trt_l + year_dummy + trt_l:year_dummy | fips 
                      + year, cluster = "state", ref_crime)
```

Panel match - probably what you wanna do to create the coefficient table

```{r}

ref_crime1 <- ref_crime %>% 
  filter(year >= "2010" & refugees > "0")

ref_crime1 <- ref_crime1 %>% 
  group_by(fips_county) %>% 
  arrange(year) %>% 
  mutate(treatedr = ifelse(year == 2017 & lag(rrefugees) > median(rrefugees), 1, 0)) %>% 
  mutate(treatedr = ifelse(year == 2018 & lag(rrefugees, 2) > median(rrefugees), 1, treatedr))

ref_crime1 <- ref_crime1 %>% 
  group_by(fips) %>% 
  arrange(year) %>% 
  mutate(treatedl = ifelse(year == 2017 & lag(lrefugees) > median(lrefugees), 1, 0)) %>% 
  mutate(treatedl = ifelse(year == 2018 & lag(lrefugees, 2) > median(lrefugees), 1, treatedl))

library(panelView)

panelView(rproperty_crime ~ treatedr, data = ref_crime1, index = c("fips","year"))

cdidr_pcrime2 <- feols(rproperty_crime ~ treatedr | fips + year, cluster = "state", ref_crime1)
summary(pcrime)


library(PanelMatch)

dta <- data.frame(fips = as.integer(ref_crime1$fips), year = as.integer(ref_crime1$year),
                   treatedr = ref_crime1$treatedr,
                   rproperty_crime = ref_crime1$rproperty_crime, fips_county = as.integer(ref_crime1$fips_county))

DisplayTreatment(unit.id = "fips_county",
                 time.id = "year", legend.position = "none",
                 xlab = "Year", ylab = "County",
                 treatment = "treatedr", data = dta)

#no matching refinement and panel estimate
PM.results.none <- PanelMatch(lag = 6, time.id = "year", 
                              unit.id = "fips", 
                              treatment = "treatedr",
                              refinement.method = "none",
                              data = dta, match.missing = TRUE,
                              size.match = 5, qoi = "att", 
                              outcome.var = "rproperty_crime",
                              lead = 0:2, forbid.treatment.reversal = FALSE,
                              use.diagonal.variance.matrix = TRUE)
msets.none <- PM.results.none$att
print(msets.none)

get_covariate_balance(PM.results.none$att,
                      data = dta3,
                      use.equal.weights = TRUE,
                      covariates = c("povrate", "vcrimerate"),
                      plot = TRUE)

PE.results.none <- PanelEstimate(sets = PM.results.none, data = dta3, 
                            se.method = "bootstrap", 
                            number.iterations = 1000,
                            confidence.level = .95)
PE.results.none[["estimates"]]
plot(PE.results.none)

```
